\chapter*{Acknowledgements}

I would like to express my gratitude to those who contributed significantly to the completion of this work. I am deeply thankful for their support, guidance, and encouragement, which will remain a precious memory of this important period in my academic and professional life.

\vspace{0.4cm}

I would first like to warmly thank Mrs. Nadège REVERDY-BRUAS, Head of the Master's program in Sustainable Printed and Integrated Electronics at INP Grenoble Pagora, for giving me the opportunity to pursue this program and for her continuous support throughout my studies.

\vspace{0.4cm}

My sincere thanks go to my supervisors, Mr. J. ALINEI and Mr. L. VILLA, from the OwnTech Foundation in Toulouse, for their availability, their valuable guidance, and the trust they placed in me throughout this project. Their advice and constructive feedback were essential to the successful completion of this work.

\vspace{0.4cm}

I would also like to thank Mr. Guillaume ARTHAUD, engineer at OwnTech, for his precious help and technical support, as well as Ayoub Farah HASSAN, PhD student who worked alongside me, for his collaboration. I wish him great success in the continuation of his research.

\vspace{0.4cm}

Finally, I would like to express my gratitude to all the teachers and staff of INP Grenoble Pagora, particularly those of the Sustainable Printed and Integrated Electronics Master's program, for the quality of the education provided and for the human values they conveyed to me throughout my studies.