\chapter*{Introduction}
\phantomsection
\addcontentsline{toc}{chapter}{Introduction}

Power electronics is a central technology for the energy transition. It makes
it possible to convert, control, and exchange electrical energy between
photovoltaic panels, batteries, motors, electrical grids, and embedded systems.
However, the design of power converters remains technically demanding because it
combines hardware design, real-time control, embedded software, measurement,
thermal management, electromagnetic compatibility, safety, and life-cycle
constraints.

\vspace{0.4cm}

This internship was carried out within the OwnTech ecosystem, whose objective
is to make power electronics more accessible through open-source hardware,
modular converter platforms, reusable software, and transparent documentation.
In this context, the work presented in this report contributes to two
complementary needs. The first one is validation: before a board can be reused
or integrated in a larger open hardware platform, its behaviour must be tested
in a repeatable and automated way. The second one is the preparation of future
high-voltage and high-power converter modules, where wide-bandgap devices such
as GaN and SiC introduce new constraints in switching speed, insulation,
thermal management, and PCB layout.

\vspace{0.4cm}

The internship work was therefore organized around two main technical projects.
The first project concerns the design and validation of the SPIN Oscilloscope
Shield, also called SPOC. It routes selected signals from a SPIN board under
test toward oscilloscope inputs. Associated firmware and Python software were
developed to automate the configuration of the board, generate test signals,
control the oscilloscope, and evaluate the measured waveforms. The goal is to
reduce manual probing and make hardware validation more systematic.

\vspace{0.4cm}

The second project concerns the design of a GaN-based Half-Bridge Board,
intended as an experimental power stage for high-speed switching tests and
future high-voltage converter development. It integrates digital isolation,
isolated auxiliary supplies, gate-driver stages, two 650~V GaN transistors, and
a compact half-bridge switching cell. Particular attention is given to reference
domains, gate driving, commutation loops, creepage and clearance distances, and
the choice of an aluminium-based insulated metal substrate.

\vspace{0.4cm}

Beyond the practical design of the boards, this report also discusses the link
between modular power electronics and sustainability. In an open-source
hardware context, sustainability is not limited to efficiency during operation.
It also depends on documentation, testability, maintainability, repairability,
upgradeability, material choices, and end-of-life recovery. The discussion on
FR4 and aluminium-based substrates is included in this perspective.

\vspace{0.4cm}

This report is organized as follows. Chapter~1 presents OwnTech, its
open-source power electronics environment, and the general internship context.
It also introduces the state of the art related to modularity, obsolescence,
documentation, and sustainable power electronics. Chapter~2 focuses on the SPOC
board, including its hardware architecture, PCB design, software environment,
automatic validation method, and experimental results. Chapter~3 presents the
GaN Half-Bridge Board, its motivation, its functional architecture, its
high-voltage and high-speed design constraints, and the discussion on
aluminium-based substrates and end-of-life considerations.